Near Optimal Behavior via Approximate State Abstraction

### 2016-02-05 paper/results_discussion.tex
Widow line

Our experimental results also highlight a noteworthy characteristic of approximate state abstraction in goal-based \acp{MDP}. Taxi exhibits relative stability in state space size and behavior for $\varepsilon$ up to $.02$, at which point both fall off dramatically. We attribute the sudden fall off of these quantities to the goal-based nature of the domain; once information critical for achieving optimal behavior is lost in the state aggregation, solving the goal---and so acquiring any reward---is impossible. Conversely, in the Random domain, a great deal of near-optimal policies are available to the agent. Thus, even as the information for optimal behavior is lost with increasng $\varepsilon$, there are many near-optimal policies available to the agent that remain available. Furthermore, as abstractions become overly aggressive, critical information may be lost such that the abstract policy may perform slightly worse than random behavior, as seen in the Random MDP.

>>>>

Our experimental results also highlight a noteworthy characteristic of approximate state abstraction in goal-based \acp{MDP}. Taxi exhibits relative stability in state space size and behavior for $\varepsilon$ up to $.02$, at which point both fall off dramatically. We attribute the sudden fall off of these quantities to the goal-based nature of the domain; once information critical for achieving optimal behavior is lost in the state aggregation, solving the goal---and so acquiring any reward---is impossible. Conversely, in the Random domain, a great deal of near-optimal policies are available to the agent. Thus, even as the information for optimal behavior is lost $\varepsilon$, there are many near-optimal policies available to the agent that remain available. Furthermore, as abstractions become overly aggressive, critical information may be lost such that the abstract policy may perform worse than random behavior, as seen in the Random MDP.
